\documentclass[9pt, a4paper]{article}

\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{wallpaper}

\usepackage{paracol}

% Do not indent paragraphs
\setlength\parindent{0in}

% \pagenumbering{gobble} does not work in this case.
% Likely due to the code for the lines needing page reference numbers.
% We use fancyhdr to modify it instead.
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % Prevent top line from appearing
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}} % Format of the page numbers

\usepackage{multicol}
\usepackage{ragged2e}



% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
%\usepackage{xunicode}
%\usepackage{xltxtra}
% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{LetterSpace=-4}
%\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Ligatures={Common}, BoldFont={Inter Semi Bold}]{Inter}
% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Inter}\selectfont\itshape\&}}
\usepackage{setspace}
\usepackage[inline]{enumitem}

\newcommand{\middot}{~\textperiodcentered~}

\setlist[itemize]{leftmargin=*} % removes margin from the itemize

\newlist{skills}{itemize*}{1}
\setlist[skills]{label={}, afterlabel={}, mode=unboxed,
itemjoin=\discretionary{}{}{\hbox{\middot}}}

\usepackage{lipsum,xcolor}
\newcommand\dunderline[3][-1pt]{{%
\sbox0{#3}%
\ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

% LANGUAGE
%--------------------------------
% Set the main language for formatting purposes, just in case.
\usepackage{polyglossia}
\setmainlanguage{en-GB}


% LINES BETWEEN ITEMS
%--------------------------------
\usepackage{tikz,tikzpagenodes}
\usetikzlibrary{calc}
\usepackage{refcount}

\newcounter{mylist} % new counter for amount of lists
\newcounter{mycnt}[mylist] % create new item counter
\newcounter{mytmp}[mylist] % tmp counter needed for checking before/after current item

\newcommand{\drawoptionsconn}{black, shorten <= .5mm, shorten >= .5mm, thick}
\newcommand{\drawoptionsshort}{black, shorten <= .5mm, shorten >= -1mm, thick}

\newcommand{\myitem}{% Modified `\item` to update counter and save nodes
	\stepcounter{mycnt}%
	\item[\linkedlist{%
		i\alph{mylist}\arabic{mycnt}}]%
	\label{item-\alph{mylist}\arabic{mycnt}}%
	\ifnum\value{mycnt}>1%
	\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}<\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
		++(0,3mm) --
		(i\alph{mylist}\arabic{mycnt} |- current page text area.north);% draw short line
	\end{tikzpicture}%
	\else%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsconn] (i\alph{mylist}\arabic{mytmp}) -- (i\alph{mylist}\arabic{mycnt});% draw the connecting lines
	\end{tikzpicture}%
	\fi%
	\fi%
	\addtocounter{mytmp}{2}%
	\IfRefUndefinedExpandable{item-\alph{mylist}\arabic{mytmp}}{}{% defined
		\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}>\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
		\begin{tikzpicture}[remember picture,overlay]%
			\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
			++(0,-3mm) --
			(i\alph{mylist}\arabic{mycnt} |- current page text area.south);% draw short line
		\end{tikzpicture}%
		\fi%
	}%
	\addtocounter{mytmp}{-1}%
}

\newcommand{\linkedlist}[1]{
	\raisebox{1.5pt}[0pt][0pt]{\begin{tikzpicture}[remember picture]%
			\node (#1) [black,circle,fill,inner sep=1.5pt]{};
	\end{tikzpicture}}%
}

\newenvironment{myitemize}{%
	% Create new `myitemize` environment to keep track of the counters
	\stepcounter{mylist}% increment list counter
	\begin{itemize}
	}{\end{itemize}%
}

\newcommand{\heading}[1]{{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \textcolor{black}{\dunderline[-3pt]{2pt}{\textbf{#1}}}}}
\newcommand{\itemheading}[1]{{\defaultfontfeatures{LetterSpace=-1}\setmainfont{Futura} \textbf{#1}}}
\newcommand{\subheading}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \textit{#1}}}
\newcommand{\monthyear}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small #1}}

\begin{document}
	{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \textcolor{black}{\centering \textbf{VINCENT LEONARDO}}}
	\columnratio{0.75}

		
		\heading{EDUCATION}
	\smallbreak
	\vspace{2pt}
	\begin{myitemize}[topsep=0ex, labelsep=0.1in]
				\begin{paracol}{2}\myitem\itemheading{Singapore University of
Technology and Design}\\\subheading{Bachelor of Engineering with Honours
(Engineering Systems and
Design)}\switchcolumn{\vspace*{5pt}\small\monthyear{SINGAPORE}\\\monthyear{MAY
2019 -- AUG 2022}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Holder of the SUTD Undergraduate Merit Scholarship.}
					\end{itemize}
			\end{myitemize}

	\vspace{0.16in}
		
		\heading{PROFESSIONAL EXPERIENCE}
	\smallbreak
	\vspace{2pt}
	\begin{myitemize}[topsep=0ex, labelsep=0.1in]
				\begin{paracol}{2}\myitem\itemheading{Regional Operations (Fraud)
Intern}\\\subheading{Shopee Pte
Ltd}\switchcolumn{\vspace*{5pt}\monthyear{SINGAPORE}\\\monthyear{MAY
2021 -- SEP 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Wrangled and examined large user behavioural
datasets using the Apache Hive ecosystem, Python, and SQL.}
						\item {\small Ideating rules that reduce instances of fraud and
conducted testing and impact analysis thereof.}
					\end{itemize}
			\end{myitemize}

	\vspace{0.16in}
		
		\heading{PROJECTS \& COMPETITIONS}
	\smallbreak
	\vspace{2pt}
	\begin{myitemize}[topsep=0pt, labelsep=0.1in]
				\begin{paracol}{2}\myitem\itemheading{The Analytics Edge Data
Competition}\\\subheading{SUTD}\switchcolumn{\item[]\monthyear{SINGAPORE}\\\monthyear{NOV
2021 -- DEC 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Group achieved first place in terms of accuracy
amongst the cohort.}
						\item {\small Developed an algorithm that determines sentiments
given a set of tweet references about the weather. Applied the RoBERTa
model in Tensorflow by translating Python code into R. Competition
required only R code.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Synthesis Sustainability IRL
Data Challenge}\\\subheading{Synthesis \&
Treatsure}\switchcolumn{\item[]\monthyear{SINGAPORE}\\\monthyear{OCT
2021 -- NOV 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Group achieved third place in the data science
challenge among around 135 participants.}
						\item {\small Modelled word associations and sentiments on food
wastage and food surplus consumption from the provided dataset to advise
Treatsure on improving ways to get more people to consume surplus food.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Classification of Myers-Briggs
Type Indicator (MBTI) Type Based on Past Posts on Internet
Forums}\\\subheading{SUTD}\switchcolumn{\item[]\monthyear{SINGAPORE}\\\monthyear{OCT
2021 -- DEC 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Used PyTorch to predict the MBTI of the
PersonalityCafe forum users based on their past fifty posts.}
						\item {\small Combined a CNN with an LSTM through experimentations
in order to obtain a weighted-averaged F1 score of 0.78 for the top six
classes. Attempted to use logistic regression, decision trees, and
ensemble models.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Agent-Based Modelling for
Airport Arrivals in a Post-Pandemic
World}\\\subheading{SUTD}\switchcolumn{\item[]\monthyear{SINGAPORE}\\\monthyear{OCT
2021 -- DEC 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Project, in the form of a web app using d3.js, was
featured in the pillar newsletter in early 2022.}
						\item {\small In charge of designing and coding the simulation
such that its use and analysis will be much more user-friendly.}
					\end{itemize}
			\end{myitemize}

	\vspace{0.16in}
	
	
	\columnratio{0.43}
	\begin{paracol}{2}
				\heading{SKILLS}
		\medbreak
		\vspace*{1pt}
		\begin{skills}
						\item {\small Data Wrangling}
						\item {\small Statistics}
						\item {\small Machine Learning\hfill}
						\item {\small Neural Networks}
						\item {\small Optimisation}
						\item {\small Simulations\hfill}
						\item {\small Creativity}
						\item {\small Problem-solving}
						\item {\small Communication\hfill}
						\item {\small Adaptability}
						\item {\small Attention to detail}
					\end{skills}

		\vspace*{0.2in}
						\heading{TOOLS}
		\medbreak
		\vspace*{1pt}
		\begin{skills}[itemsep=-0.4ex]
						\item {\small Python}
						\item {\small R}
						\item {\small JavaScript}
						\item {\small SQL}
						\item {\small Tableau}
						\item {\small \LaTeX\hfill}
						\item {\small English}
						\item {\small Bahasa Indonesia}
						\item {\small Malay}
					\end{skills}
		
		\switchcolumn

				\heading{OTHER EXPERIENCE}
		\begin{itemize}[itemsep=-0.4ex]
						\item {\small Teaching assistant for 60.002 AI Applications in
Design (2022).}
						\item {\small Participating in the Create4Good Innovation Fund
Social Venture Programme under Silver Online Society (2022).}
						\item {\small Participated in the Temasek Foundation-National
University of Singapore Leadership Enrichment and Regional Networking
Young Asian Leaders Initiative (2021).}
						\item {\small Chief Photographer, SUTD Photographic Circle
(2021--2022).}
						\item {\small Advisor, Media \& Marketing, SUTD 9th Student
Government (2021--2022).}
					\end{itemize}
			\end{paracol}
	
\end{document}