\documentclass[9pt, a4paper]{article}

\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{wallpaper}
\usepackage[hidelinks]{hyperref}
\usepackage{paracol}

% Do not indent paragraphs
\setlength\parindent{0in}

% \pagenumbering{gobble} does not work in this case.
% Likely due to the code for the lines needing page reference numbers.
% We use fancyhdr to modify it instead.
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % Prevent top line from appearing
% \rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}} % Format of the page numbers
\rfoot{} % Format of the page numbers

\usepackage{multicol}
% \usepackage{ragged2e}



% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
\usepackage{fontawesome5}
\usepackage{xunicode}
\usepackage{xltxtra}
% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{LetterSpace=-4}
%\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Ligatures={Common}, BoldFont={Inter Semi Bold}]{Inter}
% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Inter}\selectfont\itshape\&}}
\usepackage{setspace}
\usepackage[inline]{enumitem}

\newcommand{\middot}{~\textperiodcentered~}

\setlist[itemize]{leftmargin=*} % removes margin from the itemize

\newlist{skills}{itemize*}{1}
\setlist[skills]{label={}, afterlabel={}, mode=unboxed,
itemjoin=\discretionary{}{}{\hbox{\middot}}}

\usepackage{lipsum,xcolor}
\newcommand\dunderline[3][-1pt]{{%
\sbox0{#3}%
\ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

% LANGUAGE
%--------------------------------
% Set the main language for formatting purposes, just in case.
\usepackage{polyglossia}
\setmainlanguage{en-GB}


% LINES BETWEEN ITEMS
%--------------------------------
\usepackage{tikz,tikzpagenodes}
\usetikzlibrary{calc}
\usepackage{refcount}

\newcounter{mylist} % new counter for amount of lists
\newcounter{mycnt}[mylist] % create new item counter
\newcounter{mytmp}[mylist] % tmp counter needed for checking before/after current item

\newcommand{\drawoptionsconn}{black, shorten <= .5mm, shorten >= .5mm, thick}
\newcommand{\drawoptionsshort}{black, shorten <= .5mm, shorten >= -1mm, thick}

\newcommand{\myitem}{% Modified `\item` to update counter and save nodes
	\stepcounter{mycnt}%
	\item[\linkedlist{%
		i\alph{mylist}\arabic{mycnt}}]%
	\label{item-\alph{mylist}\arabic{mycnt}}%
	\ifnum\value{mycnt}>1%
	\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}<\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
		++(0,3mm) --
		(i\alph{mylist}\arabic{mycnt} |- current page text area.north);% draw short line
	\end{tikzpicture}%
	\else%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsconn] (i\alph{mylist}\arabic{mytmp}) -- (i\alph{mylist}\arabic{mycnt});% draw the connecting lines
	\end{tikzpicture}%
	\fi%
	\fi%
	\addtocounter{mytmp}{2}%
	\IfRefUndefinedExpandable{item-\alph{mylist}\arabic{mytmp}}{}{% defined
		\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}>\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
		\begin{tikzpicture}[remember picture,overlay]%
			\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
			++(0,-3mm) --
			(i\alph{mylist}\arabic{mycnt} |- current page text area.south);% draw short line
		\end{tikzpicture}%
		\fi%
	}%
	\addtocounter{mytmp}{-1}%
}

\newcommand{\linkedlist}[1]{
	\raisebox{1.5pt}[0pt][0pt]{\begin{tikzpicture}[remember picture]%
			\node (#1) [black,circle,fill,inner sep=1.5pt]{};
	\end{tikzpicture}}%
}

\newenvironment{myitemize}{%
	% Create new `myitemize` environment to keep track of the counters
	\stepcounter{mylist}% increment list counter
	\begin{itemize}
	}{\end{itemize}%
}

\newcommand{\heading}[1]{{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \textcolor{black} {\dunderline[-3pt]{2pt}{\small \textbf{#1}}}}}
\newcommand{\itemheading}[1]{{\defaultfontfeatures{LetterSpace=-2}\setmainfont{Futura} \small \textbf{#1}}}
\newcommand{\subheading}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small \textit{#1}}}
\newcommand{\monthyear}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small #1}}
\newcommand{\motto}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \footnotesize #1}}


\begin{document}
	\vspace*{0.9099in}
	\ThisCenterWallPaper{1}{cv-head-2.pdf}
	\columnratio{0.77}

		
		\heading{EDUCATION}
	\smallbreak
	\vspace{2pt}
	\begin{myitemize}[topsep=0ex, labelsep=0.1in]
				\begin{paracol}{2}\myitem\itemheading{Singapore University of
Technology and Design}\\\subheading{Bachelor of Engineering with Honours
(Engineering Systems and
Design)}\switchcolumn{\vspace*{5pt}\small\monthyear{Singapore}\\\monthyear{May
2019 -- Aug 2022}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Focusing on Artificial Intelligence-related courses
and applications.}
						\item {\small Teaching assistant for 10.020 Data Driven World
(Fall 2021) and 60.002 AI Applications in Design (Spring 2022).}
						\item {\small Awarded with the SUTD Undergraduate Merit
Scholarship.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Anglo-Chinese Junior
College}\\\subheading{GCE Advanced
Level}\switchcolumn{\vspace*{5pt}\small\monthyear{Singapore}\\\monthyear{Feb
2017 -- Dec 2018}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Obtained two distinctions.}
						\item {\small ASEAN Scholarship holder.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Anglo-Chinese School
(Independent)}\\\subheading{GCE Ordinary
Level}\switchcolumn{\vspace*{5pt}\small\monthyear{Singapore}\\\monthyear{Jan
2015 -- Dec 2016}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Obtained nine distinctions.}
						\item {\small ASEAN Scholarship holder.}
					\end{itemize}
			\end{myitemize}

	\vspace{0.16in}
		
		\heading{EXPERIENCE}
	\smallbreak
	\vspace{2pt}
	\begin{myitemize}[topsep=0ex, labelsep=0.1in]
				\begin{paracol}{2}\myitem\itemheading{Shopee Pte
Ltd}\\\subheading{Regional Operations (Fraud)
Intern}\switchcolumn{\vspace*{5pt}\monthyear{Singapore}\\\monthyear{May
2021 -- Sep 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Wrangled and examined large user behavioural
datasets using the Apache Hive ecosystem, Python, and SQL.}
						\item {\small Ideated rules that reduce instances of fraud, tested
and analysed impact thereof with three other departments.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{SUTD DManD
Centre}\\\subheading{Composites Research
Intern}\switchcolumn{\vspace*{5pt}\monthyear{Singapore}\\\monthyear{May
2020 to Sep 2020}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Optimised composites manufacturing processes and
writing ANSYS scripts to automate software simulations, laying the
groundwork for future projects.}
						\item {\small Led and collaborated with 3 researchers and 2 other
interns in various ad-hoc projects related to the research.}
						\item {\small Led equipment purchasing decisions using technical
expertise and knowledge, saving about 30-40\% of the research's budget.}
					\end{itemize}
			\end{myitemize}

	\vspace{0.16in}
		
		\heading{PROJECTS \& COMPETITIONS}
	\smallbreak
	\vspace{2pt}
	\begin{myitemize}[topsep=0pt, labelsep=0.1in]
				\begin{paracol}{2}\myitem\itemheading{Gait (or Pose) Recognition
Model and Analytics.}\\\subheading{Klass Engineering Pte
Ltd}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Jan 2022 --
Aug 2022}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Training a model to correctly identify and track a
moving person in the real world by their unique gait.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{\href{https://github.com/vincentleooo/analytics-edge-data-comp}{The Analytics Edge Data Competition}}\\\subheading{Singapore
University of Technology and
Design}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Nov 2021
-- Dec 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Headed the team of two to clinch first place in
terms of accuracy amongst the cohort.}
						\item {\small Applied the RoBERTa model in TensorFlow in R to
secure around 96\% accuracy in the sentiment classification task.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{\href{https://github.com/vincentleooo/CDS-Project-2021}{Classification of MBTI Type Based on Past Posts on Internet Forums}}\\\subheading{Singapore
University of Technology and
Design}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Oct 2021
-- Dec 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Devised model to predict the MBTI of the
PersonalityCafe forum users based on their posts within the team of
three.}
						\item {\small Merged a CNN with an LSTM using PyTorch after
experimentations involving SVM, logistic regression, decision trees,
ensemble models, and neural networks in order to achieve an accuracy of
78\% for the top six classes.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{\href{https://github.vinleonardo.com/sma-airport-model/}{Agent-Based Modelling for Airport Arrivals in a Post-Pandemic World}}\\\subheading{Singapore
University of Technology and
Design}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Oct 2021
-- Dec 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Highlighted as the top project for the course in the
\href{https://esd.sutd.edu.sg/files/ESD-Spring-Newsletter-2022.pdf}{ESD pillar newsletter}
in early 2022.}
						\item {\small Managed the team of three in designing the
architecture and user experience of the simulation using d3.js.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{\href{https://vinleonardo.com/synthesis-sustainable-competition-2021/}{Synthesis Sustainability IRL Data Challenge}}\\\subheading{Synthesis
\& Treatsure}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Oct
2021 -- Nov 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Directed the team of three to win third place in the
data science challenge among around 135 participants.}
						\item {\small Modelled word associations and sentiments on food
surplus consumption from Twitter and Instagram posts in the past five
years to consult Treatsure on persuading more people to consume surplus
food.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Count On It: A Financial
Literacy
Game}\\\subheading{SUTD}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Mar
2021 -- May 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Web app deliverable for the Engineering Systems
Architecture course.}
						\item {\small Led the technical plannings for the game
architecture and the coding process.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Optimisation of Pre-Surgery
Assessment Appointment Slots}\\\subheading{Singapore General Hospital
Pre-Admission
Centre}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Mar 2021
-- May 2021}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Partnered with client to gather and clean the
appointment data over the past three years to form statistical
inferences in R.}
						\item {\small Collaborated with team of four to implement the
M/M/s on Excel to optimise manpower, queue time, and working hours.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{Analysis of Carsharing Usage
Pattern and Utilisation}\\\subheading{Car Club Pte
Ltd}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Sep 2020 to
Dec 2020}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Guided a team of four to analyse the effects of
COVID-19 on carsharing usage using various tools such as R, SQL, Python
and GIS.}
						\item {\small Wrote Python scripts to automate the sifting and
analysis of four months of customer data provided in Excel format.}
						\item {\small Consulted the industry partner (Car Club) on
possible measures on adapting to the new behaviours found due to
COVID-19.}
					\end{itemize}
			\end{myitemize}

	\vspace{0.16in}
	
		\heading{CO-CURRICULAR ACTIVITIES}
	\smallbreak
	\vspace{2pt}
	\begin{myitemize}[topsep=0pt, labelsep=0.1in]
				\begin{paracol}{2}\myitem\itemheading{SUTD Photographic
Circle}\\\subheading{Chief
Photographer}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Feb
2021 -- Feb 2022}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Oversaw the standards of the photographs sent to the
clients over five major events.}
						\item {\small Spearheaded a film development workshop that was
fully booked within one hour.}
					\end{itemize}
				\begin{paracol}{2}\myitem\itemheading{SUTD 9th Student
Government}\\\subheading{Advisor, Media \&
Marketing}\switchcolumn{\item[]\monthyear{Singapore}\\\monthyear{Nov
2020 -- Feb 2022}}\end{paracol}
		\begin{itemize}[itemsep=-0.4ex, topsep=-0.4ex]
						\item {\small Advised and assisted the Media \& Marketing team of
seven on student engagement projects in the university.}
						\item {\small Co-led the Mental Health Awareness Week initiative,
reaching over 1000 people through videos and Telegram Stickers.}
					\end{itemize}
			\end{myitemize}

	\vspace{0.16in}
	
				\heading{SKILLS \& TOOLS}
		\medbreak
		\vspace*{1pt}
		\begin{skills}
						\item {\small Data Wrangling}
						\item {\small Visualisation}
						\item {\small Statistics}
						\item {\small Machine Learning}
						\item {\small Neural Networks}
						\item {\small Optimisation}
						\item {\small Simulations\hfill}
						\item {\small Research}
						\item {\small Python}
						\item {\small R}
						\item {\small JavaScript}
						\item {\small SQL}
						\item {\small Julia}
						\item {\small Tableau}
						\item {\small \LaTeX}
						\item {\small Adobe Suite}
						\item {\small Fusion 360}
						\item {\small English (native)\hfill}
						\item {\small Bahasa Indonesia (native)}
					\end{skills}
		
		\vspace*{0.2in}

				\heading{ADDITIONAL INFORMATION}
		\begin{itemize}[itemsep=-0.4ex]
						\item {\small Navigating through the Create4Good Innovation Fund
Social Venture Programme as part of Silver Online Society, a social
venture to help the elderly adapt to modern technology.}
						\item {\small Contributed to the Temasek Foundation-National
University of Singapore Leadership Enrichment and Regional Networking
Young Asian Leaders Initiative (2021).}
						\item {\small Enjoys history, linguistics, music, and tinkering
with technology to automate various things, including this résumé.}
					\end{itemize}
			
\end{document}