\documentclass[9pt, a4paper]{article}

\usepackage{geometry}
\geometry{a4paper, margin=0.75in}
\usepackage{wallpaper}
\usepackage[hidelinks]{hyperref}
\usepackage{paracol}

% Do not indent paragraphs
\setlength\parindent{0in}

% \pagenumbering{gobble} does not work in this case.
% Likely due to the code for the lines needing page reference numbers.
% We use fancyhdr to modify it instead.
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt} % Prevent top line from appearing
% \rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}} % Format of the page numbers
\rfoot{} % Format of the page numbers

\usepackage{multicol}
% \usepackage{ragged2e}



% TYPOGRAPHY
%--------------------------------
\usepackage{fontspec} 
\usepackage{fontawesome5}
\usepackage{xunicode}
\usepackage{xltxtra}
% converts LaTeX specials (quotes, dashes etc.) to Unicode
\defaultfontfeatures{LetterSpace=-4}
%\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Ligatures={Common}, BoldFont={Inter Semi Bold}]{Inter}
% Cool ampersand
\newcommand{\amper}{{\fontspec[Scale=.95]{Inter}\selectfont\itshape\&}}
\usepackage{setspace}
\usepackage[inline]{enumitem}

\newcommand{\middot}{~\textperiodcentered~}

\setlist[itemize]{leftmargin=*} % removes margin from the itemize

\newlist{skills}{itemize*}{1}
\setlist[skills]{label={}, afterlabel={}, mode=unboxed,
itemjoin=\discretionary{}{}{\hbox{\middot}}}

\usepackage{lipsum,xcolor}
\newcommand\dunderline[3][-1pt]{{%
\sbox0{#3}%
\ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}

% LANGUAGE
%--------------------------------
% Set the main language for formatting purposes, just in case.
\usepackage{polyglossia}
\setmainlanguage{en-GB}


% LINES BETWEEN ITEMS
%--------------------------------
\usepackage{tikz,tikzpagenodes}
\usetikzlibrary{calc}
\usepackage{refcount}

\newcounter{mylist} % new counter for amount of lists
\newcounter{mycnt}[mylist] % create new item counter
\newcounter{mytmp}[mylist] % tmp counter needed for checking before/after current item

\newcommand{\drawoptionsconn}{black, shorten <= .5mm, shorten >= .5mm, thick}
\newcommand{\drawoptionsshort}{black, shorten <= .5mm, shorten >= -1mm, thick}

\newcommand{\myitem}{% Modified `\item` to update counter and save nodes
	\stepcounter{mycnt}%
	\item[\linkedlist{%
		i\alph{mylist}\arabic{mycnt}}]%
	\label{item-\alph{mylist}\arabic{mycnt}}%
	\ifnum\value{mycnt}>1%
	\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}<\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
		++(0,3mm) --
		(i\alph{mylist}\arabic{mycnt} |- current page text area.north);% draw short line
	\end{tikzpicture}%
	\else%
	\begin{tikzpicture}[remember picture,overlay]%
		\expandafter\draw\expandafter[\drawoptionsconn] (i\alph{mylist}\arabic{mytmp}) -- (i\alph{mylist}\arabic{mycnt});% draw the connecting lines
	\end{tikzpicture}%
	\fi%
	\fi%
	\addtocounter{mytmp}{2}%
	\IfRefUndefinedExpandable{item-\alph{mylist}\arabic{mytmp}}{}{% defined
		\ifnum\getpagerefnumber{item-\alph{mylist}\arabic{mytmp}}>\getpagerefnumber{item-\alph{mylist}\arabic{mycnt}}%
		\begin{tikzpicture}[remember picture,overlay]%
			\expandafter\draw\expandafter[\drawoptionsshort] (i\alph{mylist}\arabic{mycnt}) --
			++(0,-3mm) --
			(i\alph{mylist}\arabic{mycnt} |- current page text area.south);% draw short line
		\end{tikzpicture}%
		\fi%
	}%
	\addtocounter{mytmp}{-1}%
}

\newcommand{\linkedlist}[1]{
	\raisebox{1.5pt}[0pt][0pt]{\begin{tikzpicture}[remember picture]%
			\node (#1) [black,circle,fill,inner sep=1.5pt]{};
	\end{tikzpicture}}%
}

\newenvironment{myitemize}{%
	% Create new `myitemize` environment to keep track of the counters
	\stepcounter{mylist}% increment list counter
	\begin{itemize}
	}{\end{itemize}%
}

\newcommand{\heading}[1]{{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \textcolor{black} {\dunderline[-3pt]{2pt}{\small \textbf{#1}}}}}
\newcommand{\itemheading}[1]{{\defaultfontfeatures{LetterSpace=-2}\setmainfont{Futura} \small \textbf{#1}}}
\newcommand{\subheading}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small \textit{#1}}}
\newcommand{\monthyear}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \small #1}}
\newcommand{\motto}[1]{{\defaultfontfeatures{LetterSpace=-3}\setmainfont{Futura} \footnotesize #1}}

\begin{document}
	\begin{center}
		{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \textcolor{black} {\bfseries \large VINCENT LEONARDO}}\\

		\motto{DATA \textbar{} TECHNOLOGY \textbar{} AI}\smallbreak

		{\defaultfontfeatures{LetterSpace=0}\setmainfont{Futura} \footnotesize \faEnvelope\, \href{mailto:vincent@vinleonardo.com}{vincent@vinleonardo.com} | \faPhone\, +65 8817 0611
		
		\faLinkedin\, \href{https://www.linkedin.com/in/vincentleoooo/}{vincentleoooo} | \faGlobe\, \href{https://vinleonardo.com}{vinleonardo.com} | \faGithub\, \href{https://github.com/vincentleooo/}{vincentleooo}\par}
	\end{center}
	\columnratio{0.82}
		\small
	
		
		\heading{EDUCATION}
	\smallbreak

		\itemheading{Singapore University of Technology and
Design}\begin{paracol}{2}\subheading{Bachelor of Engineering with
Honours (Engineering Systems and Design)}\switchcolumn\monthyear{May
2019 -- Aug 2022}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Focusing on Artificial Intelligence-related courses and
applications.}
				\item {Teaching assistant for 10.020 Data Driven World (Fall 2021)
and 60.002 AI Applications in Design (Spring 2022).}
				\item {Awarded with the SUTD Undergraduate Merit Scholarship.}
			\end{itemize}
	\smallbreak
	
	\smallbreak
		
		\heading{EXPERIENCE}
	\smallbreak
		\itemheading{Shopee Pte Ltd}\begin{paracol}{2}\subheading{Regional
Operations (Fraud) Intern}\switchcolumn\monthyear{May 2021 -- Sep
2021}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Wrangled and examined large user behavioural datasets using
the Apache Hive ecosystem, Python, and SQL.}
				\item {Ideated rules that reduce instances of fraud, tested and
analysed impact thereof with three other departments.}
			\end{itemize}
	\smallbreak
	
	\smallbreak
		
		\heading{PROJECTS \& COMPETITIONS}
	\smallbreak
		\itemheading{\href{https://github.com/vincentleooo/analytics-edge-data-comp}{The Analytics Edge Data Competition}}\begin{paracol}{2}\subheading{Singapore
University of Technology and Design}\switchcolumn\monthyear{Nov 2021 --
Dec 2021}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Headed the team of two to clinch first place in terms of
accuracy amongst the cohort.}
				\item {Applied the RoBERTa model in TensorFlow in R to secure around
96\% accuracy in the sentiment classification task.}
			\end{itemize}
	\smallbreak
		\itemheading{\href{https://github.com/vincentleooo/CDS-Project-2021}{Classification of MBTI Type Based on Past Posts on Internet Forums}}\begin{paracol}{2}\subheading{Singapore
University of Technology and Design}\switchcolumn\monthyear{Oct 2021 --
Dec 2021}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Devised model to predict the MBTI of the PersonalityCafe
forum users based on their posts within the team of three.}
				\item {Merged a CNN with an LSTM using PyTorch after
experimentations involving SVM, logistic regression, decision trees,
ensemble models, and neural networks in order to achieve an accuracy of
78\% for the top six classes.}
			\end{itemize}
	\smallbreak
		\itemheading{\href{https://github.vinleonardo.com/sma-airport-model/}{Agent-Based Modelling for Airport Arrivals in a Post-Pandemic World}}\begin{paracol}{2}\subheading{Singapore
University of Technology and Design}\switchcolumn\monthyear{Oct 2021 --
Dec 2021}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Highlighted as the top project for the course in the
\href{https://esd.sutd.edu.sg/files/ESD-Spring-Newsletter-2022.pdf}{ESD pillar newsletter}
in early 2022.}
				\item {Managed the team of three in designing the architecture and
user experience of the simulation using d3.js.}
			\end{itemize}
	\smallbreak
		\itemheading{\href{https://vinleonardo.com/synthesis-sustainable-competition-2021/}{Synthesis Sustainability IRL Data Challenge}}\begin{paracol}{2}\subheading{Synthesis
\& Treatsure}\switchcolumn\monthyear{Oct 2021 -- Nov 2021}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Directed the team of three to win third place in the data
science challenge among around 135 participants.}
				\item {Modelled word associations and sentiments on food surplus
consumption from Twitter and Instagram posts in the past five years to
consult Treatsure on persuading more people to consume surplus food.}
			\end{itemize}
	\smallbreak
		\itemheading{Optimisation of Pre-Surgery Assessment Appointment
Slots}\begin{paracol}{2}\subheading{Singapore General Hospital
Pre-Admission Centre}\switchcolumn\monthyear{Mar 2021 -- May
2021}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Partnered with client to gather and clean the appointment
data over the past three years to form statistical inferences in R.}
				\item {Collaborated with team of four to implement the M/M/s on
Excel to optimise manpower, queue time, and working hours.}
			\end{itemize}
	\smallbreak
	
	\smallbreak
	
		\heading{CO-CURRICULAR ACTIVITIES}
	\smallbreak
		\itemheading{SUTD Photographic
Circle}\begin{paracol}{2}\subheading{Chief
Photographer}\switchcolumn\monthyear{Feb 2021 -- Feb 2022}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Oversaw the standards of the photographs sent to the clients
over five major events.}
				\item {Spearheaded a film development workshop that was fully booked
within one hour.}
			\end{itemize}
	\smallbreak
		\itemheading{SUTD 9th Student
Government}\begin{paracol}{2}\subheading{Advisor, Media \&
Marketing}\switchcolumn\monthyear{Nov 2020 -- Feb 2022}\end{paracol}
	\begin{itemize}[itemsep=-0.3ex, topsep=0ex]
				\item {Advised and assisted the Media \& Marketing team of seven on
student engagement projects in the university.}
				\item {Co-led the Mental Health Awareness Week initiative, reaching
over 1000 people through videos and Telegram Stickers.}
			\end{itemize}
	\smallbreak
		
	\smallbreak

			\heading{SKILLS \& TOOLS}
		\smallbreak
		\vspace*{0.2ex}
		\begin{skills}
						\item {Data Wrangling}
						\item {Visualisation}
						\item {Statistics}
						\item {Machine Learning}
						\item {Neural Networks}
						\item {Optimisation}
						\item {Simulations}
						\item {Research\hfill}
						\item {Python}
						\item {R}
						\item {JavaScript}
						\item {SQL}
						\item {Julia}
						\item {Tableau}
						\item {\LaTeX}
						\item {Adobe Suite}
						\item {Fusion 360}
						\item {English (native)}
						\item {Bahasa Indonesia (native)}
					\end{skills}
		\smallbreak
		\smallbreak
		\heading{ADDITIONAL INFORMATION}
	\begin{itemize}[itemsep=-0.3ex, topsep=0.7ex]
				\item {Navigating through the Create4Good Innovation Fund Social
Venture Programme as part of Silver Online Society, a social venture to
help the elderly adapt to modern technology.}
				\item {Contributed to the Temasek Foundation-National University of
Singapore Leadership Enrichment and Regional Networking Young Asian
Leaders Initiative (2021).}
				\item {Enjoys history, linguistics, music, and tinkering with
technology to automate various things, including this résumé.}
			\end{itemize}
	\end{document}